Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-06-11 Output/manuscript/HI_Model_ms.Rmd
edited directory pathway in R script

The study area encompassed the terrestrial portion of the seven main Hawaiian Islands, a total land area of 16,464 km^2^ (Figure 1). This land area was subdivided into a grid of 250 x 250 m simulation cells. The state type of each simulation cell was based on combinations of three Moisture Zones, seven Islands, and ten discrete land cover classes (Figure 1).

```{r fig.align = 'center', out.width = "80%", fig.cap = "Land cover map of the seven main Hawaiian Islands, adapted from Jacobi et al. (2017). Agriculture in this map combines herbaceous and woody crops, but these two crop types are treated as separate land cover classes in the simulation model. Land cover classes not shown: Water, Wetland."}
knitr::include_graphics("./fig_images/fig1_HI_LC.png").
```

>>>>

The study area encompassed the terrestrial portion of the seven main Hawaiian Islands, a total land area of 16,464 km^2^ (Figure 1). This land area was subdivided into a grid of 250 x 250 m simulation cells. Each simulation cell was assigned to one of 210 possible state types based on the unique combination of three Moisture Zones (Figure S1), seven Islands, and ten discrete land cover classes (Figure 1).

```{r fig.align = 'center', out.width = "80%", fig.cap = "Land cover map of the seven main Hawaiian Islands, adapted from Jacobi et al. (2017). Agriculture in this map combines herbaceous and woody crops, but these two crop types are treated as separate land cover classes in the simulation model. Water and Wetland land cover classes are not shown."}
knitr::include_graphics("./fig_images/fig1_HI_LC.png").
```
